---
title: "stats_7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# clean workspace
rm(list=ls())

if (!require("pacman")) install.packages("pacman")
pacman::p_load(ggplot2, dplyr, lm.beta, RColorBrewer, nationalparkcolors, rjson, reticulate, gridExtra, wesanderson, MASS, outliers, lmerTest, stringr, lmPerm, glmnet)

# set up python for later
use_python("/Users/stiso/anaconda3/bin/python") # path to python binary
py_config() # check it is using the specified version

# directory for RAM data, request from XXX
RAM_dir = '/Volumes/bassett-data/Jeni/RAM/'

# parameters
win = 1
detector = ''

```


Tests on betas

```{r}
net_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/net_data_clean', detector, '.csv',sep=''))
net_data$race = as.factor(net_data$race)
soz_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/net_soz_data_clean', detector ,'.csv',sep=''))
soz_data$race = as.factor(soz_data$race)
soz_data <- mutate(soz_data, band_measure = paste(Frequency.Band, Measure, sep = '_'))
spike_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/net_spike_data_clean', detector, '.csv',sep=''))
spike_data$race = as.factor(spike_data$race)
spike_data <- mutate(spike_data, band_measure = paste(Frequency.Band, Measure, sep = '_'))

```

Are distributions of effect sizes different from 0?
```{r}
pred = 'bin'# bin or num or spr
aec_flag = 'aec$' # which aec do you want to EXCLUDE, orth or regular. The carrot mean "starts with", $                      means 'ends with'
coh_flag = '^coh' # 
plv_flag = 'iplv$'

curr_measures = net_data[!grepl(aec_flag, net_data$Measure) & !grepl(coh_flag, net_data$Measure) & !grepl(plv_flag, net_data$Measure), 'band_measure']
bfc = unique(curr_measures)
ps = list()
ts = list()
df = list()
for (m in bfc){
  print(m)
  curr <- filter(net_data, band_measure == m)
  y = unlist(na.omit(curr[paste('str_beta_', pred, sep='')]))
  stat <- t.test(y)
  print(stat)
  ps = c(ps, stat$p.value)
  ts = c(ts, stat$statistic)
  df = c(df, stat$parameter)
}

# corrections based on aec or aec_orth, not both
stats = data.frame(p = p.adjust(ps, method='bonferroni'), t = unlist(ts), df = unlist(df), measure = bfc, sig = p.adjust(ps, method="bonferroni") < 0.05)
stats

```
```{r}
pred = 'spr'# bin or num or spr
aec_flag = 'aec$' # which aec do you want to EXCLUDE, orth or regular. The carrot mean "starts with", $                      means 'ends with'
coh_flag = '^coh' # 
plv_flag = 'iplv$'

curr_measures = net_data[!grepl(aec_flag, net_data$Measure) & !grepl(coh_flag, net_data$Measure) & !grepl(plv_flag, net_data$Measure), 'band_measure']
bfc = unique(curr_measures)
ps = list()
ts = list()
df = list()
for (m in bfc){
  print(m)
  curr <- filter(net_data, band_measure == m)
  y = unlist(na.omit(curr[paste('ti_beta_', pred, sep='')]))
  stat <- t.test(y)
  print(stat)
  ps = c(ps, stat$p.value)
  ts = c(ts, stat$statistic)
  df = c(df, stat$parameter)
}

# corrections based on aec or aec_orth, not both
stats = data.frame(p = p.adjust(ps, method='bonferroni'), t = unlist(ts), df = unlist(df), measure = bfc, sig = p.adjust(ps, method="bonferroni") < 0.05)
stats

```


Is there a differences between orthogonalized AEC, and AEC, of coh and imaginary coh, etc?
```{r}
pred = 'bin'
m = 'plv'

# test for main effect of orthogonalization
if (m == 'aec'){
  amp = filter(net_data, Measure == 'aec' | Measure == 'aec_ortho')
} else if (m == 'coh') {
  amp = filter(net_data, Measure == 'coh' | Measure == 'im_coh')
} else {
  amp = filter(net_data, Measure == 'plv' | Measure == 'iplv')
}

bands = unique(amp$Frequency.Band)
aec_ps = list()
aec_ts = list()
aec_df = list()

for (m in bands){
  print(m)
  curr <- dplyr::filter(amp, Frequency.Band == m)
  if (pred == 'bin'){
    stat <- lmer(data=curr, str_beta_bin ~ Measure + (1|subj))
  } else {
    stat <- lmer(data=curr, str_beta_num ~ Measure + (1|subj))
  }
  print(anova(stat))
  aec_ps = c(aec_ps, anova(stat)$`Pr(>F)`[1])
  aec_ts = c(aec_ts, anova(stat)$`F value`[1])
  aec_df = c(aec_df, anova(stat)$DenDF[1])
}

aec_stats = data.frame(p = unlist(aec_ps), f = unlist(aec_ts), df = unlist(aec_df), band = bands, sigMC = p.adjust(aec_ps, method = 'bonferroni') < 0.05, sig = aec_ps < 0.05)
aec_stats
```

Do distributions of effect sizes differ within seizure onset zone vs outside of it?
```{r}
pred = 'num'
aec_flag = 'aec$' # which aec do you want to EXCLUDE, orth or regular. The carrot mean "starts with", $                      means 'ends with'
coh_flag = '^coh' # 
plv_flag = '^plv'

soz_data$band_measure = tolower(soz_data$band_measure)
curr_measures = soz_data[!grepl(aec_flag, soz_data$Measure) & !grepl(coh_flag, soz_data$Measure) & !grepl(plv_flag, soz_data$Measure), 'band_measure']
curr_measures = curr_measures[curr_measures != 'high gamma_iplv']

pred = paste('soz_beta_', pred, sep = '')
soz_bm = unique(curr_measures)
soz_ps = list()
soz_ts = list()
soz_df = list()
for (m in soz_bm){
  print(m)
  curr <- dplyr::filter(soz_data, band_measure == m)
  within <- dplyr::filter(curr, SOZ == 'within') 
  within <- dplyr::select(within, pred)
  outside <- dplyr::filter(curr, SOZ == 'outside')
  outside <- dplyr::select(outside, pred)
  stat <- t.test(within[,1], outside[,1], paired=TRUE)
  print(stat)
  soz_ps = c(soz_ps, stat$p.value)
  soz_ts = c(soz_ts, stat$statistic)
  soz_df = c(soz_df, stat$parameter)
}

soz_stats = data.frame(p = unlist(soz_ps), t = unlist(soz_ts), df = unlist(soz_df), measure = soz_bm, sigMC = p.adjust(soz_ps, method="bonferroni") < 0.05, sig = unlist(soz_ps) < 0.05)
soz_stats

```

```{r}
pred = 'num'
aec_flag = 'aec$' # which aec do you want to EXCLUDE, orth or regular. The carrot mean "starts with", $                      means 'ends with'
coh_flag = '^coh' # 
plv_flag = '^plv'

spike_data$band_measure = tolower(spike_data$band_measure)
curr_measures = spike_data[!grepl(aec_flag, spike_data$Measure) & !grepl(coh_flag, spike_data$Measure) & !grepl(plv_flag, spike_data$Measure), 'band_measure']
curr_measures = curr_measures[curr_measures != 'high gamma_iplv']

pred = paste('spike_beta_', pred, sep = '')
spike_bm = unique(curr_measures)
spike_ps = list()
spike_ts = list()
spike_df = list()
for (m in spike_bm){
  print(m)
  curr <- dplyr::filter(spike_data, band_measure == m)
  within <- dplyr::filter(curr, spike == 'present') 
  within <- dplyr::select(within, pred)
  outside <- dplyr::filter(curr, spike == 'absent')
  outside <- dplyr::select(outside, pred)
  stat <- t.test(within[,1], outside[,1], paired=TRUE)
  print(stat)
  spike_ps = c(spike_ps, stat$p.value)
  spike_ts = c(spike_ts, stat$statistic)
  spike_df = c(spike_df, stat$parameter)
}

spike_stats = data.frame(p = unlist(spike_ps), t = unlist(spike_ts), df = unlist(spike_df), measure = spike_bm, sigMC = p.adjust(spike_ps, method="bonferroni") < 0.05, sig = unlist(spike_ps) < 0.05)
spike_stats

```
Similarity across predictors
```{r}
pred1 = 'spr'# bin or num or spr
pred2 = 'bin'
aec_flag = 'aec$' # which aec do you want to EXCLUDE, orth or regular. The carrot mean "starts with", $                      means 'ends with'
coh_flag = '^coh' # 
plv_flag = 'iplv$'

curr_measures = net_data[!grepl(aec_flag, net_data$Measure) & !grepl(coh_flag, net_data$Measure) & !grepl(plv_flag, net_data$Measure), 'band_measure']
bfc = unique(curr_measures)
ps = list()
rs = list()
ns = list()
measures=list()
for (m in bfc){
  print(m)
  curr <- filter(net_data, band_measure == m)
  stat <- cor.test(unlist(curr[paste('str_beta_', pred1, sep='')]), unlist(curr[paste('str_beta_', pred2, sep='')]), method='spearman')
  print(stat)
  ps = c(ps, stat$p.value)
  rs = c(rs, stat$estimate)
  ns = c(ns, min(c(length(na.omit(unlist(curr[paste('str_beta_', pred1, sep='')]))), length(na.omit(unlist(curr[paste('str_beta_', pred2, sep='')]))))))
  measures = c(measures, curr$Measure[1])
}

# corrections based on aec or aec_orth, not both
stats_pred = data.frame(p = p.adjust(ps, method='bonferroni'), r = unlist(rs), n = unlist(ns), measure = bfc, meas = unlist(measures), sig = p.adjust(ps, method="bonferroni") < 0.05)
stats_pred

```
```{r}
plot_data = dplyr::summarize(group_by(stats_pred, meas), meanr = mean(r), semr = sqrt(var(r)/length(r)), meanp = mean(p))
plot_data$meas = factor(plot_data$meas, levels=c(2,5,7,8,3))

g = ggplot(plot_data, aes(x=meas, y=meanr, fill=meas)) +
  geom_bar(stat='identity') + geom_errorbar(aes(ymin=meanr-semr, ymax=meanr+semr), width=.2) +
  theme_minimal() + scale_fill_manual(values=park_palette('Acadia',5)[c(2,4,5,3,1)]) + ylim(-.1,.8)
g
ggsave(paste('../img/pred_sim', pred1, '_', pred2, '.pdf', sep=''))

```

The rest of the stats are concerning parsing variability across indidividuals and channels
```{r}
net_data <-mutate(net_data, band_measure_clean = tolower(paste(Frequency.Band, Measure, sep = '_')))
keep_measures = c('theta_aec_ortho', 'theta_im_coh', 'alpha_aec_ortho',  'beta_aec_ortho', 'beta_im_coh', 'gamma_aec_ortho', 'gamma_im_coh', 'high gamma_aec_ortho',
                  'high gamma_im_coh')
bm = unique(net_data$band_measure_clean)
supp_measures = bm[which(!bm %in% keep_measures)]

node_keep_measures = c('theta_aec_ortho', 'theta_im_coh','alpha_aec_ortho',  'beta_aec_ortho', 'beta_im_coh', 'gamma_aec_ortho', 'gamma_im_coh', 'hg_aec_ortho', 
                       'hg_im_coh')

```


 # Relationship with behavior

 
```{r}
 # general task performance
pred = 'bin'
supp_flag = FALSE # are you using main measures, or supplemental measures

task_ps = list()
task_df = list()
task_ts = list()
tasks = c('TH', 'YC', 'PAL', 'FR', 'catFR')
net_task_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/net_task_data_clean', detector, '.csv', sep=''))
net_task_data$race <- as.factor(net_task_data$race)
net_task_data <- mutate(net_task_data, band_measure = paste(Frequency.Band, Measure, sep = '_'))
net_task_data$band_measure <- tolower(net_task_data$band_measure)
if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    net_task_data = dplyr::filter(net_task_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    net_task_data = dplyr::filter(net_task_data, band_measure != m)
  }
}
fc = unique(net_task_data$band_measure)
fc = fc[fc != 'high gamma_iplv']

for (m in fc){
  print(m)
  curr = dplyr::filter(net_task_data, band_measure == m)
  curr = curr[!is.na(curr[,paste('str_beta_', pred, sep='')]),]
  nObs = dim(curr)[1]
  nRow = dim(resid)[1]
  fit = lm(data=curr, paste('pca1 ~ str_beta_', pred, '+ race + gender + age + hand + Education + Etiology + SeizureAge', sep=''))
  print(anova(fit))
      
  # get stats
  task_ps = c(task_ps, summary(fit)$coefficients[2,'Pr(>|t|)'])
  task_ts = c(task_ts, summary(fit)$coefficients[2,'t value'])
  task_df = c(task_df, summary(fit)$df[2])
}

task_stats = data.frame(p = unlist(task_ps), f = unlist(task_ts), df = unlist(task_df), band_measure = fc, sigMC = p.adjust(task_ps, method = 'bonferroni') < 0.05, sig = task_ps < 0.05)
task_stats
```
```{r}
# save residuals
 # general task performance
supp_flag = FALSE # are you using main measures, or supplemental measures

subj = list()
band_measures = list()
resids = list()
bands = list()
tasks = c('TH', 'YC', 'PAL', 'FR', 'catFR')
net_task_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/net_task_data_clean', detector, '.csv', sep=''))
net_task_data$race <- as.factor(net_task_data$race)
net_task_data <- mutate(net_task_data, band_measure = paste(Frequency.Band, Measure, sep = '_'))
net_task_data$band_measure <- tolower(net_task_data$band_measure)
if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    net_task_data = dplyr::filter(net_task_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    net_task_data = dplyr::filter(net_task_data, band_measure != m)
  }
}
fc = unique(net_task_data$band_measure)
fc = fc[fc != 'high gamma_iplv']

for (m in fc){
  print(m)
  curr = dplyr::filter(net_task_data, band_measure == m)
  curr = na.omit(curr[,c('subj', 'band_measure', 'Frequency.Band', 'Measure', 'pca1', 'Etiology', 'race', 'gender', 'age', 'hand', 'Education', 'SeizureAge')])
  nObs = dim(curr)[1]
  nRow = dim(resid)[1]
  fit = lm(data=curr, pca1~race + gender + age + hand + Education + Etiology + SeizureAge)

  # get stats
  subj = c(subj, as.character(curr$subj))
  band_measures = c(band_measures, curr$band_measure)
  bands = c(bands, as.character(curr$Frequency.Band))
  resids = c(resids, fit$residuals)
}

task_resid = data.frame(subj = unlist(subj), band_measure = unlist(band_measures), resid = unlist(resids), band = bands)
write.csv(task_resid, paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/net_task_data_resid', detector, '.csv', sep=''))
```

# With demographics

```{r}
pred = 'bin'
supp_flag = FALSE
idx = 4 # which demographic do you want to make plots for? use the index for the 'dems' list. 1 = race, 2 = gender, etc

dems = c('race', 'gender', 'hand', 'age')
dem_ps = list()
dem_ts = list()
dem_df = list()
curr = net_data
if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    curr = dplyr::filter(curr, band_measure_clean != m)
  }
}else {
  for (m in supp_measures){
    curr = dplyr::filter(curr, band_measure_clean != m)
  }
}
fc = unique(curr$band_measure)
for (m in fc){
  print(m)
  fit = lm(data=dplyr::filter(curr, band_measure == m), paste('str_beta_',pred,' ~ race + gender + hand + age',sep=''))
  print(anova(fit))
  dem_ps = c(dem_ps, anova(fit)$`Pr(>F)`[idx])
  dem_ts = c(dem_ts, anova(fit)$`F value`[idx])
  dem_df = c(dem_df, anova(fit)$Df[idx])
}
dem_stats = data.frame(dem = dems[idx], p = unlist(dem_ps), f = unlist(dem_ts), df = unlist(dem_df), band_measure = fc, sigMC = p.adjust(dem_ps, method = 'bonferroni') < 0.05, sig = dem_ps < 0.05)
dem_stats
```

# variability in SOZ/spike location
```{r}
pred = 'bin'
supp_flag = FALSE # are you using main measures, or supplemental measures
flag = 'spike'

loc_ps = list()
loc_df = list()
loc_ts = list()
soz_loc_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/sys_',flag, detector, '.csv', sep=''))
soz_loc_data <- mutate(soz_loc_data, band_measure = tolower(paste(Frequency.Band, Measure, sep = '_')))
if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    soz_loc_data = dplyr::filter(soz_loc_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    soz_loc_data = dplyr::filter(soz_loc_data, band_measure != m)
  }
}
fc = unique(soz_loc_data$band_measure)
for (m in fc){
  print(m)
  curr = dplyr::filter(soz_loc_data,  band_measure == m)
  if (pred == 'num'){
    fit = aovp(data=curr, str_beta_num ~ locus + race + gender + hand + age + Etiology + Lesional + Education + SeizureAge + contacts)
  } else if (pred == 'bin') {
    fit = aovp(data=curr, str_beta_bin ~ locus + race + gender + hand + age + Etiology + Lesional + Education + SeizureAge + contacts)
  } else
    fit = aovp(data=curr, str_beta_spr ~ locus + race + gender + hand + age + Etiology + Lesional + Education + SeizureAge  + contacts)
  print(anova(fit))
  loc_ps = c(loc_ps, summary(fit)[[1]]$`Pr(Prob)`[1])
  loc_ts = c(loc_ts, summary(fit)[[1]]$`R Mean Sq`[1])
  loc_df = c(loc_df, summary(fit)[[1]]$Df[1])
}

loc_stats = data.frame(p = unlist(loc_ps), f = unlist(loc_ts), df = unlist(loc_df), band_measure = fc, sigMC = p.adjust(loc_ps, method = 'bonferroni') < 0.05, sig = loc_ps < 0.05)
loc_stats

```
```{r}
fit = aovp(data=curr, str_beta_num ~ locus + race + gender + hand + age)
summary(fit)

```

## Pathology
# lesional vs nonlesional
```{r}
pred = 'spr'
supp_flag = FALSE # are you using main measures, or supplemental measures

les_ps = list()
les_df = list()
les_ts = list()
les_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/clinical', detector, '.csv', sep=''))
les_data <- mutate(les_data, band_measure = tolower(paste(Frequency.Band, Measure, sep = '_')))

if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    les_data = dplyr::filter(les_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    les_data = dplyr::filter(les_data, band_measure != m)
  }
}
fc = unique(les_data$band_measure)
for (m in fc){
  print(m)
  curr = dplyr::filter(les_data, band_measure == m)
  if (pred == 'num'){
    fit = aovp(data=curr, str_beta_num ~ Lesional + race + gender + age)
  } else if (pred == 'bin') {
    fit = aovp(data=curr, str_beta_bin ~ Lesional + race + gender + age)
  } else {
    fit = aovp(data=curr, str_beta_spr ~ Lesional + race + gender + age)
  }
  
  print(summary(fit))
  tmp <- summary(fit)
  les_ps = c(les_ps, summary(fit)[[1]]$`Pr(Prob)`[1])
  les_ts = c(les_ts, summary(fit)[[1]]$`R Mean Sq`[1])
  les_df = c(les_df, summary(fit)[[1]]$Df[1])
}

les_stats = data.frame(p = unlist(les_ps), f = unlist(les_ts), df = unlist(les_df), band_measure = fc, sigMC = p.adjust(les_ps, method = 'bonferroni') < 0.05, sig = les_ps < 0.05)
les_stats

```

# etiology
```{r}
pred = 'bin'
supp_flag = FALSE # are you using main measures, or supplemental measures

clin_ps = list()
clin_df = list()
clin_ts = list()
clin_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/clinical', detector, '.csv', sep=''))
clin_data <- mutate(clin_data, band_measure = tolower(paste(Frequency.Band, Measure, sep = '_')))
# drop categories that have less than X people
value_counts = as.data.frame(table(clin_data[clin_data$band_measure == 'alpha_aec_ortho',]$Etiology))
idx = value_counts$Freq > 10
keep_vars = value_counts[idx,'Var1']
clin_data = clin_data[unlist(lapply(clin_data$Etiology, function(x) any(grepl(x, keep_vars)))),]
# remove 'unkown'
clin_data = dplyr::filter(clin_data, Etiology != 'Unknown' & Etiology != 'Other')
if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    clin_data = dplyr::filter(clin_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    clin_data = dplyr::filter(clin_data, band_measure != m)
  }
}
fc = unique(clin_data$band_measure)
for (m in fc){
  print(m)
  curr = dplyr::filter(clin_data, band_measure == m)
  if (pred == 'num'){
    fit = aovp(data=curr, str_beta_num ~ locus + hem + race + gender + hand + age + Etiology + Lesional + Education + SeizureAge + contacts + Institution)
  } else if (pred == 'bin') {
    fit = aovp(data=curr, str_beta_bin ~ locus + hem + race + gender + hand + age + Etiology + Lesional + Education + SeizureAge + contacts + Institution)
  } else {
    fit = aovp(data=curr, str_beta_spr ~ locus + hem + race + gender + hand + age + Etiology + Lesional + Education + SeizureAge + contacts + Institution)
  }
  
  print(summary(fit))
  tmp <- summary(fit)
  clin_ps = c(clin_ps, summary(fit)[[1]]$`Pr(Prob)`[1])
  clin_ts = c(clin_ts, summary(fit)[[1]]$`R Mean Sq`[1])
  clin_df = c(clin_df, summary(fit)[[1]]$Df[1])
}

clin_stats = data.frame(p = unlist(clin_ps), f = unlist(clin_ts), df = unlist(clin_df), band_measure = fc, sigMC = p.adjust(clin_ps, method = 'bonferroni') < 0.05, sig = clin_ps < 0.05)
clin_stats

```


## Which variables explain the most variance
# first show that none are significant
```{r}
pred = 'bin'
supp_flag = FALSE # are you using main measures, or supplemental measures


all_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/net_dem_data', detector, '.csv', sep=''))
all_data <- mutate(all_data, band_measure = tolower(paste(Frequency.Band, Measure, sep = '_')))
all_data[paste('str_beta_',pred,sep='')] = as.numeric(unlist(all_data[paste('str_beta_',pred,sep='')]))
if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    all_data = dplyr::filter(all_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    all_data = dplyr::filter(all_data, band_measure != m)
  }
}
fc = unique(all_data$band_measure)
for (m in fc){
  print(m)
  curr = dplyr::filter(all_data, band_measure == m)
  if (pred == 'num'){
    fit = aovp(data=curr, str_beta_num ~ locus + hem + race + gender + hand + age + Etiology + Lesional + SeizureAge + contacts + Institution)
  } else if (pred == 'bin') {
    fit = aovp(data=curr, str_beta_bin ~ locus  + race + gender + age + Etiology + Lesional + SeizureAge + contacts  + hem)
  } else {
    fit = aovp(data=curr, str_beta_spr ~ locus + hem + race + gender + hand + age + Etiology + Lesional + SeizureAge + contacts + Institution)
  }
  
  print(summary(fit))
}


```
# fit ridge regression
```{r}
pred = 'bin'
supp_flag = FALSE # are you using main measures, or supplemental measures


all_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/net_dem_data', detector, '.csv', sep=''))
all_data <- mutate(all_data, band_measure = tolower(paste(Frequency.Band, Measure, sep = '_')))
all_data[paste('str_beta_',pred,sep='')] = as.numeric(unlist(all_data[paste('str_beta_',pred,sep='')]))
all_data[c('age','Education','SeizureAge')] = as.numeric(unlist(all_data[c('age','Education','SeizureAge')]))
if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    all_data = dplyr::filter(all_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    all_data = dplyr::filter(all_data, band_measure != m)
  }
}
fc = unique(all_data$band_measure)
for (m in fc){
  print(m)
  curr = dplyr::filter(all_data, band_measure == m)
  curr = curr[!is.na(curr[,paste('str_beta_',pred,sep='')]),]
  x = model.matrix(~locus + hem + race + gender + age + Etiology + Lesional + SeizureAge + contacts + Institution + hand + Education, curr)[, -1]
  groups = c(rep(1,each=7),rep(2,each=2),rep(3,each=3),rep(4,each=2),5,rep(6,each=9),rep(7,each=2),8,rep(9,each=3),rep(10,each=7),rep(11,each=4),12)
  if (pred == 'num'){
    y = unlist(curr$str_beta_num)
    fit = gglasso(x=x,y=y,group=groups)
  } else if (pred == 'bin') {
    y = unlist(curr$str_beta_bin)
    fit = gglasso(x=x,y=y,group=groups)
  } else {
    y = unlist(curr$str_beta_spr)
    fit = gglasso(x=x,y=y,group=groups)
  }
  
}


```
## Parsing Variability across regions

# aggregating over systems

```{r}

supp_flag = FALSE # is this analysis for the supplemental meausres, or the main ones
pred = 'bin'

sys_ps = list()
sys_df = list()
sys_ndf = list()
sys_fs = list()
sys_data = read.csv(paste(RAM_dir, 'group_analysis/win_', as.character(win), '/sys_stats', detector, '.csv', sep=''))
sys_data <- mutate(sys_data, band_measure = tolower(paste(band, fc_measure, sep = '_')))
if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    sys_data = dplyr::filter(sys_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    sys_data = dplyr::filter(sys_data, band_measure != m)
  }
}

fc = unique(sys_data$band_measure)
for (m in fc){
  print(m)
  if (pred == 'bin'){
    fit = lmer(data=dplyr::filter(sys_data, band_measure == m), scale_bin ~ sys + (1|subj))
  } else if (pred == 'num') {
    fit = lmer(data=dplyr::filter(sys_data, band_measure == m), scale_num ~ sys + (1|subj))
  } else {
    fit = lmer(data=dplyr::filter(sys_data, band_measure == m), scale_spr ~ sys + (1|subj))
  }
  print(anova(fit))
  sys_ps = c(sys_ps, anova(fit)$`Pr(>F)`[1])
  sys_fs = c(sys_fs, anova(fit)$`F value`[1])
  sys_ndf = c(sys_ndf, anova(fit)$NumDF[1])
  sys_df = c(sys_df, anova(fit)$DenDF[1])
}

sys_stats = data.frame(p = unlist(sys_ps), f = unlist(sys_fs), ndf = unlist(sys_ndf), df = unlist(sys_df), band_measure = fc, sigMC = p.adjust(sys_ps, method = 'bonferroni') < 0.05, sig = sys_ps < 0.05)
sys_stats
```

# aggregating by electrode type
```{r}

supp_flag = FALSE # is this analysis for the supplemental meausres, or the main ones
pred = 'bin'

wm_ps = list()
wm_df = list()
wm_ndf = list()
wm_fs = list()
wm_data = read.csv(paste(RAM_dir, 'group_analysis/win_', as.character(win), '/type_stats', detector, '.csv', sep=''))
wm_data <- mutate(wm_data, band_measure = paste(band, fc_measure, sep = '_'))
if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    wm_data = dplyr::filter(wm_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    wm_data = dplyr::filter(wm_data, band_measure != m)
  }
}

fc = unique(sys_data$band_measure)
for (m in fc){
  print(m)
  if (pred == 'bin'){
    fit = lmer(data=dplyr::filter(wm_data, band_measure == m), str_beta_bin ~ type + (1|subj))
  } else {
    fit = lmer(data=dplyr::filter(wm_data, band_measure == m), str_beta_num ~ type + (1|subj))
  }
  print(anova(fit))
  wm_ps = c(wm_ps, anova(fit)$`Pr(>F)`[1])
  wm_fs = c(wm_fs, anova(fit)$`F value`[1])
  wm_ndf = c(wm_ndf, anova(fit)$NumDF[1])
  wm_df = c(wm_df, anova(fit)$DenDF[1])
}

wm_stats = data.frame(p = unlist(wm_ps), f = unlist(wm_fs), ndf = unlist(wm_ndf), df = unlist(wm_df), band_measure = fc, sigMC = p.adjust(wm_ps, method = 'bonferroni') < 0.05, sig = wm_ps < 0.05)
wm_stats
```

## EDA

```{python}
# imports
import numpy as np
import pandas as pd
import seaborn as sns

# directories
RAM_dir = '/Volumes/bassett-data/Jeni/RAM/'

# load data
net_data = pd.read_csv(RAM_dir + 'group_analysis/network_stats.csv')
node_data = pd.read_csv(RAM_dir + 'group_analysis/node_stats.csv')

node_data.head()
```


Tests on betas

```{r}
net_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/net_data_clean', detector, '.csv',sep=''))
net_data$race = as.factor(net_data$race)
soz_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/net_soz_data_clean', detector ,'.csv',sep=''))
soz_data$race = as.factor(soz_data$race)
soz_data <- mutate(soz_data, band_measure = paste(Frequency.Band, Measure, sep = '_'))
spike_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/net_spike_data_clean', detector, '.csv',sep=''))
spike_data$race = as.factor(spike_data$race)
spike_data <- mutate(spike_data, band_measure = paste(Frequency.Band, Measure, sep = '_'))

```

Are distributions of effect sizes different from 0?
```{r}
pred = 'num'# bin or num
aec_flag = 'aec$' # which aec do you want to EXCLUDE, orth or regular. The carrot mean "starts with", $                      means 'ends with'
coh_flag = '^coh' # 

curr_measures = net_data[!grepl(aec_flag, net_data$Measure) & !grepl(coh_flag, net_data$Measure),'band_measure']
bfc = unique(curr_measures)
ps = list()
ts = list()
df = list()
for (m in bfc){
  print(m)
  curr <- filter(net_data, band_measure == m)
  stat <- t.test(curr[paste('str_beta_', pred, sep='')])
  print(stat)
  ps = c(ps, stat$p.value)
  ts = c(ts, stat$statistic)
  df = c(df, stat$parameter)
}

# corrections based on aec or aec_orth, not both
stats = data.frame(p = p.adjust(ps, method='bonferroni'), t = unlist(ts), df = unlist(df), measure = bfc, sig = p.adjust(ps, method="bonferroni") < 0.05)
stats

```

Is there a differences between orthogonalized AEC, and AEC, of coh and imaginary coh?
```{r}
pred = 'num'
m = 'coh'

# test for main effect of orthogonalization
if (m == 'aec'){
  amp = filter(net_data, Measure == 'aec' | Measure == 'aec_ortho')
} else {
  amp = filter(net_data, Measure == 'coh' | Measure == 'im_coh')
}

bands = unique(amp$Frequency.Band)
aec_ps = list()
aec_ts = list()
aec_df = list()

for (m in bands){
  print(m)
  curr <- dplyr::filter(amp, Frequency.Band == m)
  if (pred == 'bin'){
    stat <- lmer(data=curr, str_beta_bin ~ Measure + (1|subj))
  } else {
    stat <- lmer(data=curr, str_beta_num ~ Measure + (1|subj))
  }
  print(anova(stat))
  aec_ps = c(aec_ps, anova(stat)$`Pr(>F)`[1])
  aec_ts = c(aec_ts, anova(stat)$`F value`[1])
  aec_df = c(aec_df, anova(stat)$DenDF[1])
}

aec_stats = data.frame(p = unlist(aec_ps), f = unlist(aec_ts), df = unlist(aec_df), band = bands, sigMC = p.adjust(aec_ps, method = 'bonferroni') < 0.05, sig = aec_ps < 0.05)
aec_stats
```

Do distributions of effect sizes differ within seizure onset zone vs outside of it?
```{r}
pred = 'bin'
aec_flag = 'aec$' # which aec do you want to EXCLUDE, orth or regular. The carrot mean "starts with", $                      means 'ends with'
coh_flag = '^coh' # 

curr_measures = soz_data[!grepl(aec_flag, soz_data$Measure) & !grepl(coh_flag, soz_data$Measure),'band_measure']

pred = paste('soz_beta_', pred, sep = '')
soz_bm = unique(curr_measures)
soz_ps = list()
soz_ts = list()
soz_df = list()
for (m in soz_bm){
  print(m)
  curr <- dplyr::filter(soz_data, band_measure == m)
  within <- dplyr::filter(curr, SOZ == 'within') 
  within <- dplyr::select(within, pred)
  outside <- dplyr::filter(curr, SOZ == 'outside')
  outside <- dplyr::select(outside, pred)
  stat <- t.test(within[,1], outside[,1], paired=TRUE)
  print(stat)
  soz_ps = c(soz_ps, stat$p.value)
  soz_ts = c(soz_ts, stat$statistic)
  soz_df = c(soz_df, stat$parameter)
}

soz_stats = data.frame(p = unlist(soz_ps), t = unlist(soz_ts), df = unlist(soz_df), measure = soz_bm, sigMC = p.adjust(soz_ps, method="bonferroni") < 0.05, sig = unlist(soz_ps) < 0.05)
soz_stats

```

```{r}
pred = 'bin'
aec_flag = 'aec$' # which aec do you want to EXCLUDE, orth or regular. The carrot mean "starts with", $                      means 'ends with'
coh_flag = '^coh' # 

curr_measures = spike_data[!grepl(aec_flag, spike_data$Measure) & !grepl(coh_flag, spike_data$Measure),'band_measure']

pred = paste('spike_beta_', pred, sep = '')
spike_bm = unique(curr_measures)
spike_ps = list()
spike_ts = list()
spike_df = list()
for (m in spike_bm){
  print(m)
  curr <- dplyr::filter(spike_data, band_measure == m)
  within <- dplyr::filter(curr, spike == 'present') 
  within <- dplyr::select(within, pred)
  outside <- dplyr::filter(curr, spike == 'absent')
  outside <- dplyr::select(outside, pred)
  stat <- t.test(within[,1], outside[,1], paired=TRUE)
  print(stat)
  spike_ps = c(spike_ps, stat$p.value)
  spike_ts = c(spike_ts, stat$statistic)
  spike_df = c(spike_df, stat$parameter)
}

spike_stats = data.frame(p = unlist(spike_ps), t = unlist(spike_ts), df = unlist(spike_df), measure = spike_bm, sigMC = p.adjust(spike_ps, method="bonferroni") < 0.05, sig = unlist(spike_ps) < 0.05)
spike_stats

```

The rest of the stats are concerning parsing variability across indidividuals and channels
```{r}
net_data <-mutate(net_data, band_measure_clean = tolower(paste(Frequency.Band, Measure, sep = '_')))
keep_measures = c('theta_aec_ortho', 'lfp_ar', 'alpha_im_coh', 'beta_im_coh', 'gamma_im_coh')
bm = unique(net_data$band_measure_clean)
supp_measures = bm[which(!bm %in% keep_measures)]
```


 # Relationship with behavior

 
```{r}
 # general task performance
pred = 'num'
supp_flag = FALSE # are you using main measures, or supplemental measures

task_ps = list()
task_df = list()
task_ts = list()
tasks = c('TH', 'YC', 'PAL', 'FR', 'catFR')
net_task_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/net_task_data_clean', detector, '.csv', sep=''))
net_task_data$race <- as.factor(net_task_data$race)
net_task_data <- mutate(net_task_data, band_measure = paste(Frequency.Band, Measure, sep = '_'))
net_task_data$band_measure <- tolower(net_task_data$band_measure)
if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    net_task_data = dplyr::filter(net_task_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    net_task_data = dplyr::filter(net_task_data, band_measure != m)
  }
}
fc = unique(net_task_data$band_measure)
for (m in fc){
  print(m)
  curr = dplyr::filter(net_task_data, band_measure == m)
  curr = curr[!is.na(curr[,paste('str_beta_', pred, sep='')]),]
  nObs = dim(curr)[1]
  nRow = dim(resid)[1]
  fit = lm(data=curr, paste('avg ~ str_beta_', pred, '+ race + gender + age + hand + Etiology + Education + SeizureAge', sep=''))
  print(anova(fit))
      
  # get stats
  task_ps = c(task_ps, summary(fit)$coefficients[2,'Pr(>|t|)'])
  task_ts = c(task_ts, summary(fit)$coefficients[2,'t value'])
  task_df = c(task_df, summary(fit)$df[2])
}

task_stats = data.frame(p = unlist(task_ps), f = unlist(task_ts), df = unlist(task_df), band_measure = fc, sigMC = p.adjust(task_ps, method = 'bonferroni') < 0.05, sig = task_ps < 0.05)
task_stats
```


```{r}
resid = data.frame(subj = character(length=0), Measure = character(length=0), resid_num = numeric(0), resid_bin = numeric(0), Band = character(length=0), nav = numeric(0), recall = numeric(0), stringsAsFactors = FALSE)
```
```{r}
 # general task performance
pred = 'bin'

net_task_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/net_task_data_clean', detector, '.csv', sep=''))
net_task_data$race = as.factor(net_task_data$race)
net_task_data <- mutate(net_task_data, band_measure = paste(Frequency.Band, Measure, sep = '_'))

fc = unique(net_task_data$band_measure)
for (m in fc){
  curr = dplyr::filter(net_task_data, band_measure == m)
  curr = curr[rowSums(is.na(curr[,c(paste('str_beta_', pred, sep=''),'Education','SeizureAge','Etiology')])) == 0,]
  nObs = dim(curr)[1]
  nRow = dim(resid)[1]
  # scale
  fit = lm(data=curr, paste('str_beta_', pred, ' ~ avg + race + gender + age + hand + Etiology + Education + SeizureAge', sep=''))

  # get residuals
  resid[(nRow+1):(nRow+nObs),'subj'] = as.character(curr$subj)
  resid[(nRow+1):(nRow+nObs),'Measure'] = as.character(curr$Measure)
  resid[(nRow+1):(nRow+nObs),'Band'] = as.character(curr$Frequency.Band)
  resid[(nRow+1):(nRow+nObs), 'nav'] = curr$scale_nav
  resid[(nRow+1):(nRow+nObs), 'recall'] = curr$recall
  if (pred == 'num'){
    resid[(nRow+1):(nRow+nObs), 'resid_num'] = fit$residuals
  } else {
    resid[(nRow+1):(nRow+nObs), 'resid_bin'] = fit$residuals
  }

}

```

```{r}
# save residuals for plots
write.csv(resid, file = paste(RAM_dir, 'group_analysis/win_', as.character(win), '/resid', detector, '.csv', sep=''))
```

```{r}
pred = 'bin'
task = 'nav' #nav or recall, individual tasks are TH, FR, catFR, PAL, YC
supp_flag = FALSE # are you using main measures, or supplemental measures

task_ps = list()
task_df = list()
task_ts = list()
tasks = c('TH', 'YC', 'PAL', 'FR', 'catFR')
net_task_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/net_task_data_clean', detector, '.csv', sep=''))
net_task_data$race = as.factor(net_task_data$race)
net_task_data <- mutate(net_task_data, band_measure = paste(Frequency.Band, Measure, sep = '_'))
net_task_data$band_measure <- tolower(net_task_data$band_measure)
if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    net_task_data = dplyr::filter(net_task_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    net_task_data = dplyr::filter(net_task_data, band_measure != m)
  }
}
fc = unique(net_task_data$band_measure)
for (m in fc){
  print(m)
  curr = dplyr::filter(net_task_data, band_measure == m)
  # scale
  contrasts(curr$gender) <- contr.helmert(2)/2
  fit = lm(data=curr, paste(task, ' ~ str_beta_', pred, ' + race + gender + age + hand + avg + Etiology + SeizureAge + Education', sep=''))
  print(anova(fit))
  task_ps = c(task_ps, summary(fit)$coefficients[2,'Pr(>|t|)'])
  task_ts = c(task_ts, summary(fit)$coefficients[2,'t value'])
  task_df = c(task_df, summary(fit)$df[2])
}

task_stats = data.frame(p = unlist(task_ps), f = unlist(task_ts), df = unlist(task_df), band_measure = fc, sigMC = p.adjust(task_ps, method = 'bonferroni') < 0.05, sig = task_ps < 0.05)
task_stats
```



# With demographics

```{r}
pred = 'num'
supp_flag = FALSE
idx = 4 # which demographic do you want to make plots for? use the index for the 'dems' list. 1 = race, 2 = gender, etc

dems = c('race', 'gender', 'hand', 'age')
dem_ps = list()
dem_ts = list()
dem_df = list()
curr = net_data
if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    curr = dplyr::filter(curr, band_measure_clean != m)
  }
}else {
  for (m in supp_measures){
    curr = dplyr::filter(curr, band_measure_clean != m)
  }
}
fc = unique(curr$band_measure)
for (m in fc){
  print(m)
  fit = lm(data=dplyr::filter(curr, band_measure == m), paste('str_beta_',pred,' ~ race + gender + hand + age',sep=''))
  print(anova(fit))
  dem_ps = c(dem_ps, anova(fit)$`Pr(>F)`[idx])
  dem_ts = c(dem_ts, anova(fit)$`F value`[idx])
  dem_df = c(dem_df, anova(fit)$Df[idx])
}
dem_stats = data.frame(dem = dems[idx], p = unlist(dem_ps), f = unlist(dem_ts), df = unlist(dem_df), band_measure = fc, sigMC = p.adjust(dem_ps, method = 'bonferroni') < 0.05, sig = dem_ps < 0.05)
dem_stats
```

# variability in soz hemisphere
```{r}
pred = 'num'
supp_flag = FALSE # are you using main measures, or supplemental measures
flag = 'spike' # do you want to look at soz or spike

hem_ps = list()
hem_df = list()
hem_ts = list()
hem_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/sys_',flag, detector, '.csv', sep=''))
hem_data <- mutate(hem_data, band_measure = tolower(paste(Frequency.Band, Measure, sep = '_')))
hem_data$hem_hand[!((hem_data$hem_hand == 'i') | (hem_data$hem_hand == 'c'))] = NA

if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    hem_data = dplyr::filter(hem_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    hem_data = dplyr::filter(hem_data, band_measure != m)
  }
}
fc = unique(hem_data$band_measure)
for (m in fc){
  print(m)
  curr = dplyr::filter(hem_data, band_measure == m)
  if (pred == 'num'){
    fit = aovp(data=curr, str_beta_num ~ hem_hand + race + gender + age)
  } else {
    fit = aovp(data=curr, str_beta_bin ~ hem_hand + race + gender + age)
  }
  
  print(summary(fit))
  tmp <- summary(fit)
  hem_ps = c(hem_ps, summary(fit)[[1]]$`Pr(Prob)`[1])
  hem_ts = c(hem_ts, summary(fit)[[1]]$`R Mean Sq`[1])
  hem_df = c(hem_df, summary(fit)[[1]]$Df[1])
}

hem_stats = data.frame(p = unlist(hem_ps), f = unlist(hem_ts), df = unlist(hem_df), band_measure = fc, sigMC = p.adjust(hem_ps, method = 'bonferroni') < 0.05, sig = hem_ps < 0.05)
hem_stats

```
# variability in SOZ/spike location
```{r}
pred = 'bin'
supp_flag = FALSE # are you using main measures, or supplemental measures
flag = 'spike'

loc_ps = list()
loc_df = list()
loc_ts = list()
soz_loc_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/sys_',flag, detector, '.csv', sep=''))
soz_loc_data <- mutate(soz_loc_data, band_measure = tolower(paste(Frequency.Band, Measure, sep = '_')))
if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    soz_loc_data = dplyr::filter(soz_loc_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    soz_loc_data = dplyr::filter(soz_loc_data, band_measure != m)
  }
}
fc = unique(soz_loc_data$band_measure)
for (m in fc){
  print(m)
  curr = dplyr::filter(soz_loc_data, band_measure == m)
  if (pred == 'num'){
    fit = aovp(data=curr, str_beta_num ~ locus + race + gender + hand + age)
  } else {
    fit = aovp(data=curr, str_beta_bin ~ locus + race + gender + hand + age)
  }
  print(summary(fit))
  loc_ps = c(loc_ps, summary(fit)[[1]]$`Pr(Prob)`[1])
  loc_ts = c(loc_ts, summary(fit)[[1]]$`R Mean Sq`[1])
  loc_df = c(loc_df, summary(fit)[[1]]$Df[1])
}

loc_stats = data.frame(p = unlist(loc_ps), f = unlist(loc_ts), df = unlist(loc_df), band_measure = fc, sigMC = p.adjust(loc_ps, method = 'bonferroni') < 0.05, sig = loc_ps < 0.05)
loc_stats

```
## Pathology
# lesional vs nonlesional
```{r}
pred = 'num'
supp_flag = FALSE # are you using main measures, or supplemental measures

les_ps = list()
les_df = list()
les_ts = list()
les_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/clinical', detector, '.csv', sep=''))
les_data <- mutate(les_data, band_measure = tolower(paste(Frequency.Band, Measure, sep = '_')))

if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    les_data = dplyr::filter(les_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    les_data = dplyr::filter(les_data, band_measure != m)
  }
}
fc = unique(les_data$band_measure)
for (m in fc){
  print(m)
  curr = dplyr::filter(les_data, band_measure == m)
  if (pred == 'num'){
    fit = aovp(data=curr, str_beta_num ~ Leisional + race + gender + age)
  } else {
    fit = aovp(data=curr, str_beta_bin ~ Lesional + race + gender + age)
  }
  
  print(summary(fit))
  tmp <- summary(fit)
  les_ps = c(les_ps, summary(fit)[[1]]$`Pr(Prob)`[1])
  les_ts = c(les_ts, summary(fit)[[1]]$`R Mean Sq`[1])
  les_df = c(les_df, summary(fit)[[1]]$Df[1])
}

les_stats = data.frame(p = unlist(les_ps), f = unlist(les_ts), df = unlist(les_df), band_measure = fc, sigMC = p.adjust(les_ps, method = 'bonferroni') < 0.05, sig = les_ps < 0.05)
les_stats

```

# etiology
```{r}
pred = 'bin'
supp_flag = FALSE # are you using main measures, or supplemental measures

clin_ps = list()
clin_df = list()
clin_ts = list()
clin_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/clinical', detector, '.csv', sep=''))
clin_data <- mutate(clin_data, band_measure = tolower(paste(Frequency.Band, Measure, sep = '_')))
# drop categories that have less than 10 people
value_counts = as.data.frame(table(clin_data[clin_data$band_measure == 'alpha_aec',]$Etiology))
idx = value_counts$Freq > 5
keep_vars = value_counts[idx,'Var1']
clin_data = clin_data[unlist(lapply(clin_data$Etiology, function(x) any(grepl(x, keep_vars)))),]
# remove 'unkown'
clin_data = dplyr::filter(clin_data, Etiology != 'Unkown')
if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    clin_data = dplyr::filter(clin_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    clin_data = dplyr::filter(clin_data, band_measure != m)
  }
}
fc = unique(clin_data$band_measure)
for (m in fc){
  print(m)
  curr = dplyr::filter(clin_data, band_measure == m)
  if (pred == 'num'){
    fit = aovp(data=curr, str_beta_num ~ Etiology + race + gender + age)
  } else {
    fit = aovp(data=curr, str_beta_bin ~ Etiology + race + gender + age)
  }
  
  print(summary(fit))
  tmp <- summary(fit)
  clin_ps = c(clin_ps, summary(fit)[[1]]$`Pr(Prob)`[1])
  clin_ts = c(clin_ts, summary(fit)[[1]]$`R Mean Sq`[1])
  clin_df = c(clin_df, summary(fit)[[1]]$Df[1])
}

clin_stats = data.frame(p = unlist(clin_ps), f = unlist(clin_ts), df = unlist(clin_df), band_measure = fc, sigMC = p.adjust(clin_ps, method = 'bonferroni') < 0.05, sig = clin_ps < 0.05)
clin_stats

```



## Parsing Variability across regions

```{r}
sys_data = read.csv(paste(RAM_dir, 'group_analysis/win_', as.character(win), '/sys_stats', detector, '.csv', sep=''))
sys_data <- mutate(sys_data, band_measure = tolower(paste(band, fc_measure, sep = '_')))
bm = unique(sys_data$band_measure)
node_supp_measures = bm[which(!bm %in% node_keep_measures)]
```

# aggregating over systems

```{r}

supp_flag = FALSE # is this analysis for the supplemental meausres, or the main ones
pred = 'spr'

sys_ps = list()
sys_df = list()
sys_ndf = list()
sys_fs = list()
sys_data = read.csv(paste(RAM_dir, 'group_analysis/win_', as.character(win), '/sys_stats', detector, '.csv', sep=''))
sys_data <- mutate(sys_data, band_measure = tolower(paste(band, fc_measure, sep = '_')))
if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in node_keep_measures){
    sys_data = dplyr::filter(sys_data, band_measure != m)
  }
}else {
  for (m in node_supp_measures){
    sys_data = dplyr::filter(sys_data, band_measure != m)
  }
}

fc = unique(sys_data$band_measure)
for (m in fc){
  print(m)
  if (pred == 'bin'){
    fit = lmer(data=dplyr::filter(sys_data, band_measure == m), scale_bin ~ sys + (1|subj))
  } else if (pred == 'num') {
    fit = lmer(data=dplyr::filter(sys_data, band_measure == m), scale_num ~ sys + (1|subj))
  } else {
    fit = lmer(data=dplyr::filter(sys_data, band_measure == m), scale_spr ~ sys + (1|subj))
  }
  print(anova(fit))
  sys_ps = c(sys_ps, anova(fit)$`Pr(>F)`[1])
  sys_fs = c(sys_fs, anova(fit)$`F value`[1])
  sys_ndf = c(sys_ndf, anova(fit)$NumDF[1])
  sys_df = c(sys_df, anova(fit)$DenDF[1])
}

sys_stats = data.frame(p = unlist(sys_ps), f = unlist(sys_fs), ndf = unlist(sys_ndf), df = unlist(sys_df), band_measure = fc, sigMC = p.adjust(sys_ps, method = 'bonferroni') < 0.05, sig = sys_ps < 0.05)
sys_stats
```

# aggregating by electrode type
```{r}

supp_flag = FALSE # is this analysis for the supplemental meausres, or the main ones
pred = 'spr'

wm_ps = list()
wm_df = list()
wm_ndf = list()
wm_fs = list()
wm_data = read.csv(paste(RAM_dir, 'group_analysis/win_', as.character(win), '/type_stats', detector, '.csv', sep=''))
wm_data <- mutate(wm_data, band_measure = paste(band, fc_measure, sep = '_'))
if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in node_keep_measures){
    wm_data = dplyr::filter(wm_data, band_measure != m)
  }
}else {
  for (m in node_supp_measures){
    wm_data = dplyr::filter(wm_data, band_measure != m)
  }
}

fc = unique(sys_data$band_measure)
for (m in fc){
  print(m)
  if (pred == 'bin'){
    fit = lmer(data=dplyr::filter(wm_data, band_measure == m), str_beta_bin ~ type + (1|subj))
  } else if (pred == 'num'){
    fit = lmer(data=dplyr::filter(wm_data, band_measure == m), str_beta_num ~ type + (1|subj))
  } else {
    fit = lmer(data=dplyr::filter(wm_data, band_measure == m), str_beta_spr ~ type + (1|subj))
  }
  print(anova(fit))
  wm_ps = c(wm_ps, anova(fit)$`Pr(>F)`[1])
  wm_fs = c(wm_fs, anova(fit)$`F value`[1])
  wm_ndf = c(wm_ndf, anova(fit)$NumDF[1])
  wm_df = c(wm_df, anova(fit)$DenDF[1])
}

wm_stats = data.frame(p = unlist(wm_ps), f = unlist(wm_fs), ndf = unlist(wm_ndf), df = unlist(wm_df), band_measure = fc, sigMC = p.adjust(wm_ps, method = 'bonferroni') < 0.05, sig = wm_ps < 0.05)
wm_stats
```
