---
title: "stats_7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# clean workspace
rm(list=ls())

if (!require("pacman")) install.packages("pacman")
pacman::p_load(ggplot2, dplyr, lm.beta, RColorBrewer, nationalparkcolors, rjson, reticulate, gridExtra, wesanderson, MASS, outliers, lmerTest, stringr, lmPerm, glmnet, gglasso, car, EnvStats)

# set up python for later
use_python("/Users/stiso/anaconda3/bin/python") # path to python binary
py_config() # check it is using the specified version

# directory for RAM data, request from XXX
RAM_dir = '/Volumes/bassett-data/Jeni/RAM/'

# parameters
win = 1
detector = ''

```


Tests on betas

```{r}
net_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/net_data_clean', detector, '.csv',sep=''))
net_data$race = as.factor(net_data$race)
soz_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/net_soz_data_clean', detector ,'.csv',sep=''))
soz_data$race = as.factor(soz_data$race)
soz_data <- mutate(soz_data, band_measure = paste(Frequency.Band, Measure, sep = '_'))
spike_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/net_spike_data_clean', detector, '.csv',sep=''))
spike_data$race = as.factor(spike_data$race)
spike_data <- mutate(spike_data, band_measure = paste(Frequency.Band, Measure, sep = '_'))

```

Are distributions of effect sizes different from 0?
```{r}
pred = 'spr'# bin or num or spr
aec_flag = 'aec$' # which aec do you want to EXCLUDE, orth or regular. The carrot mean "starts with", $                      means 'ends with'
coh_flag = '^coh' # 
plv_flag = '^plv$'

curr_measures = net_data[!grepl(aec_flag, net_data$Measure) & !grepl(coh_flag, net_data$Measure) & !grepl(plv_flag, net_data$Measure), 'band_measure']
bfc = unique(curr_measures)
ps = list()
ts = list()
df = list()
for (m in bfc){
  print(m)
  curr <- filter(net_data, band_measure == m)
  y = unlist(na.omit(curr[paste('str_beta_', pred, sep='')]))
  stat <- oneSamplePermutationTest(y)
  print(stat)
  ps = c(ps, stat$p.value)
  ts = c(ts, stat$statistic)
  df = c(df, stat$sample.size)
}

# corrections based on aec or aec_orth, not both
stats = data.frame(p = p.adjust(ps, method='bonferroni'), t = unlist(ts), df = unlist(df), measure = bfc, sig = p.adjust(ps, method="bonferroni") < 0.05)
stats

```
# Same for skew
```{r}
pred = 'spr'# bin or num or spr
aec_flag = 'aec$' # which aec do you want to EXCLUDE, orth or regular. The carrot mean "starts with", $                      means 'ends with'
coh_flag = '^coh' # 
plv_flag = 'iplv$'

curr_measures = net_data[!grepl(aec_flag, net_data$Measure) & !grepl(coh_flag, net_data$Measure) & !grepl(plv_flag, net_data$Measure), 'band_measure']
bfc = unique(curr_measures)
ps = list()
ts = list()
df = list()
for (m in bfc){
  print(m)
  curr <- filter(net_data, band_measure == m)
  y = unlist(na.omit(curr[paste('ti_beta_', pred, sep='')]))
  stat <- oneSamplePermutationTest(y)
  print(stat)
  ps = c(ps, stat$p.value)
  ts = c(ts, stat$statistic)
  df = c(df, stat$sample.size)
}

# corrections based on aec or aec_orth, not both
stats = data.frame(p = p.adjust(ps, method='bonferroni'), t = unlist(ts), df = unlist(df), measure = bfc, sig = p.adjust(ps, method="bonferroni") < 0.05)
stats

```


Is there a differences between orthogonalized AEC, and AEC, of coh and imaginary coh, etc?
```{r}
pred = 'bin'
m = 'plv'

# test for main effect of orthogonalization
if (m == 'aec'){
  amp = filter(net_data, Measure == 'aec' | Measure == 'aec_ortho')
} else if (m == 'coh') {
  amp = filter(net_data, Measure == 'coh' | Measure == 'im_coh')
} else {
  amp = filter(net_data, Measure == 'plv' | Measure == 'iplv')
}

bands = unique(amp$Frequency.Band)
aec_ps = list()
aec_ts = list()
aec_df = list()

for (m in bands){
  print(m)
  curr <- dplyr::filter(amp, Frequency.Band == m)
  if (pred == 'bin'){
    stat <- lmer(data=curr, str_beta_bin ~ Measure + (1|subj))
  } else {
    stat <- lmer(data=curr, str_beta_num ~ Measure + (1|subj))
  }
  print(anova(stat))
  aec_ps = c(aec_ps, anova(stat)$`Pr(>F)`[1])
  aec_ts = c(aec_ts, anova(stat)$`F value`[1])
  aec_df = c(aec_df, anova(stat)$DenDF[1])
}

aec_stats = data.frame(p = unlist(aec_ps), f = unlist(aec_ts), df = unlist(aec_df), band = bands, sigMC = p.adjust(aec_ps, method = 'bonferroni') < 0.05, sig = aec_ps < 0.05)
aec_stats
```

Do distributions of effect sizes differ within seizure onset zone vs outside of it?
```{r}
pred = 'spr'
aec_flag = 'aec$' # which aec do you want to EXCLUDE, orth or regular. The carrot mean "starts with", $                      means 'ends with'
coh_flag = '^coh' # 
plv_flag = '^plv'

soz_data$band_measure = tolower(soz_data$band_measure)
curr_measures = soz_data[!grepl(aec_flag, soz_data$Measure) & !grepl(coh_flag, soz_data$Measure) & !grepl(plv_flag, soz_data$Measure), 'band_measure']
curr_measures = curr_measures[curr_measures != 'high gamma_iplv']

pred = paste('soz_diff_', pred, sep = '')
soz_bm = unique(curr_measures)
soz_ps = list()
soz_ts = list()
soz_df = list()
for (m in soz_bm){
  print(m)
  curr <- dplyr::filter(soz_data, band_measure == m)
  stat <- oneSamplePermutationTest(unlist(curr[pred]))
  print(stat)
  soz_ps = c(soz_ps, stat$p.value)
  soz_ts = c(soz_ts, stat$statistic)
  soz_df = c(soz_df, stat$sample.size)
}

soz_stats = data.frame(p = p.adjust(soz_ps, method="bonferroni"), t = unlist(soz_ts), df = unlist(soz_df), measure = soz_bm, sigMC = p.adjust(soz_ps, method="bonferroni") < 0.05, sig = unlist(soz_ps) < 0.05)
soz_stats

```
# repeat for spikes
```{r}
pred = 'spr'
aec_flag = 'aec$' # which aec do you want to EXCLUDE, orth or regular. The carrot mean "starts with", $                      means 'ends with'
coh_flag = '^coh' # 
plv_flag = '^plv'

spike_data$band_measure = tolower(spike_data$band_measure)
curr_measures = spike_data[!grepl(aec_flag, spike_data$Measure) & !grepl(coh_flag, spike_data$Measure) & !grepl(plv_flag, spike_data$Measure), 'band_measure']
curr_measures = curr_measures[curr_measures != 'high gamma_iplv']

pred = paste('spike_diff_', pred, sep = '')
spike_bm = unique(curr_measures)
spike_ps = list()
spike_ts = list()
spike_df = list()
for (m in spike_bm){
  print(m)
  curr <- dplyr::filter(spike_data, band_measure == m)
  stat <- oneSamplePermutationTest(unlist(curr[pred]))
  print(stat)
  spike_ps = c(spike_ps, stat$p.value)
  spike_ts = c(spike_ts, stat$statistic)
  spike_df = c(spike_df, stat$sample.size)
}

spike_stats = data.frame(p = p.adjust(spike_ps, method="bonferroni"), t = unlist(spike_ts), df = unlist(spike_df), measure = spike_bm, sigMC = p.adjust(spike_ps, method="bonferroni") < 0.05, sig = unlist(spike_ps) < 0.05)
spike_stats

```
```{r}
pred = 'spr'
aec_flag = 'aec$' # which aec do you want to EXCLUDE, orth or regular. The carrot mean "starts with", $                      means 'ends with'
coh_flag = '^coh' # 
plv_flag = '^plv'

spike_data$band_measure = tolower(spike_data$band_measure)
curr_measures = spike_data[!grepl(aec_flag, spike_data$Measure) & !grepl(coh_flag, spike_data$Measure) & !grepl(plv_flag, spike_data$Measure), 'band_measure']
curr_measures = curr_measures[curr_measures != 'high gamma_iplv']

pred = paste('str_not_spike_beta_', pred, sep = '')
spike_bm = unique(curr_measures)
spike_ps = list()
spike_ts = list()
spike_df = list()
for (m in spike_bm){
  print(m)
  curr <- dplyr::filter(spike_data, band_measure == m)
  stat <- oneSamplePermutationTest(unlist(curr[pred]))
  print(stat)
  spike_ps = c(spike_ps, stat$p.value)
  spike_ts = c(spike_ts, stat$statistic)
  spike_df = c(spike_df, stat$sample.size)
}

spike_stats = data.frame(p = unlist(p.adjust(spike_ps, method="bonferroni")), t = unlist(spike_ts), df = unlist(spike_df), measure = spike_bm, sigMC = p.adjust(spike_ps, method="bonferroni") < 0.05, sig = unlist(spike_ps) < 0.05)
spike_stats

```
Similarity across predictors
```{r}
pred1 = 'num'# bin or num or spr
pred2 = 'spr'
aec_flag = 'aec$' # which aec do you want to EXCLUDE, orth or regular. The carrot mean "starts with", $                      means 'ends with'
coh_flag = '^coh' # 
plv_flag = '^plv'
curr_measures = net_data[!grepl(aec_flag, net_data$Measure) & !grepl(coh_flag, net_data$Measure) & !grepl(plv_flag, net_data$Measure), 'band_measure']
bfc = unique(curr_measures)
ps = list()
rs = list()
ns = list()
measures=list()
for (m in bfc){
  print(m)
  curr <- filter(net_data, band_measure == m)
  stat <- cor.test(unlist(curr[paste('str_beta_', pred1, sep='')]), unlist(curr[paste('str_beta_', pred2, sep='')]), method='spearman')
  print(stat)
  ps = c(ps, stat$p.value)
  rs = c(rs, stat$estimate)
  ns = c(ns, min(c(length(na.omit(unlist(curr[paste('str_beta_', pred1, sep='')]))), length(na.omit(unlist(curr[paste('str_beta_', pred2, sep='')]))))))
  measures = c(measures, curr$Measure[1])
}
# corrections based on aec or aec_orth, not both
stats_pred = data.frame(p = p.adjust(ps, method='bonferroni'), r = unlist(rs), n = unlist(ns), measure = bfc, meas = unlist(measures), sig = p.adjust(ps, method="bonferroni") < 0.05)
stats_pred
```

```{r}
plot_data = dplyr::summarize(group_by(stats_pred, meas), meanr = mean(r), semr = sqrt(var(r)/length(r)), meanp = mean(p))
plot_data$meas = factor(plot_data$meas, levels=c(2,5,6,8,3))
g = ggplot(plot_data, aes(x=meas, y=meanr, fill=meas)) +
  geom_bar(stat='identity') + geom_errorbar(aes(ymin=meanr-semr, ymax=meanr+semr), width=.2) +
  theme_minimal() + scale_fill_manual(values=park_palette('Acadia',5)[c(2,4,5,3,1)]) + ylim(-.1,.8)
g
ggsave(paste('../img/pred_sim', pred1, '_', pred2, '.pdf', sep=''))
```

The rest of the stats are concerning parsing variability across indidividuals and channels
```{r}
net_data <-mutate(net_data, band_measure_clean = tolower(paste(Frequency.Band, Measure, sep = '_')))
keep_measures = c('theta_aec_ortho', 'theta_im_coh', 'alpha_aec_ortho', 'alpha_im_coh', 'beta_aec_ortho', 'beta_im_coh', 'gamma_aec_ortho', 'gamma_im_coh', 'high gamma_aec_ortho',
                  'high gamma_im_coh')
bm = unique(net_data$band_measure_clean)
supp_measures = bm[which(!bm %in% keep_measures)]
node_keep_measures = c('theta_aec_ortho', 'theta_im_coh','alpha_aec_ortho',  'beta_aec_ortho', 'beta_im_coh', 'gamma_aec_ortho', 'gamma_im_coh', 'hg_aec_ortho', 
                       'hg_im_coh')
```

# does coverage type matter
```{r}
pred = 'spr'
supp_flag = FALSE # are you using main measures, or supplemental measures

cov_ps = list()
cov_df = list()
cov_ts = list()
cov_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/clinical', detector, '.csv', sep=''))
cov_data <- mutate(cov_data, band_measure = tolower(paste(Frequency.Band, Measure, sep = '_')))

if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    cov_data = dplyr::filter(cov_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    cov_data = dplyr::filter(cov_data, band_measure != m)
  }
}
fc = unique(cov_data$band_measure)
for (m in fc){
  print(m)
  curr = dplyr::filter(cov_data, band_measure == m)
  if (pred == 'num'){
    fit = aovp(data=filter(curr, contacts != 'M'), str_beta_num ~ contacts + race + gender + hand + age + Institution)
  } else if (pred == 'bin') {
    fit = aovp(data=filter(curr, contacts != 'M'), str_beta_bin ~ contacts + race + gender + hand + age + Institution)
  } else {
    fit = aovp(data=filter(curr, contacts != 'M'), str_beta_spr ~ contacts + race + gender + hand + age + Institution)
  }
  
  print(summary(fit))
  tmp <- summary(fit)
  cov_ps = c(cov_ps, summary(fit)[[1]]$`Pr(Prob)`[1])
  cov_ts = c(cov_ts, summary(fit)[[1]]$`R Mean Sq`[1])
  cov_df = c(cov_df, summary(fit)[[1]]$Df[1])
}

cov_stats = data.frame(p = unlist(cov_ps), f = unlist(cov_ts), df = unlist(cov_df), band_measure = fc, sigMC = p.adjust(cov_ps, method = 'bonferroni') < 0.05, sig = cov_ps < 0.05)
cov_stats

```

# does wm or gm matter
```{r}
pred = 'bin'
supp_flag = FALSE # are you using main measures, or supplemental measures

wm_ps = list()
wm_df = list()
wm_ts = list()
wm_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/clinical', detector, '.csv', sep=''))
wm_data <- mutate(wm_data, band_measure = tolower(paste(Frequency.Band, Measure, sep = '_')))

if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    wm_data = dplyr::filter(wm_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    wm_data = dplyr::filter(wm_data, band_measure != m)
  }
}
fc = unique(wm_data$band_measure)
for (m in fc){
  print(m)
  curr = dplyr::filter(wm_data, band_measure == m)
  if (pred == 'num'){
    fit = oneSamplePermutationTest(unlist(curr$wm_diff_num))
  } else if (pred == 'bin') {
    fit = oneSamplePermutationTest(unlist(curr$wm_diff_bin))
  } else {
    fit = oneSamplePermutationTest(unlist(curr$wm_diff_spr))
  }
  
  print(summary(fit))
  wm_ps = c(wm_ps, fit$p.value)
  wm_ts = c(wm_ts, fit$statistic)
  wm_df = c(wm_df, fit$sample.size)
}

wm_stats = data.frame(p = unlist(wm_ps), f = unlist(wm_ts), df = unlist(wm_df), band_measure = fc, sigMC = p.adjust(wm_ps, method = 'bonferroni') < 0.05, sig = wm_ps < 0.05)
wm_stats

```


# within a person, does coverage type matter
```{r}
pred = 'bin'
supp_flag = FALSE # are you using main measures, or supplemental measures

cov_wi_ps = list()
cov_wi_df = list()
cov_wi_ts = list()
cov_wi_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/clinical', detector, '.csv', sep=''))
cov_wi_data <- mutate(cov_wi_data, band_measure = tolower(paste(Frequency.Band, Measure, sep = '_')))

if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    cov_wi_data = dplyr::filter(cov_wi_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    cov_wi_data = dplyr::filter(cov_wi_data, band_measure != m)
  }
}
fc = unique(cov_wi_data$band_measure)
for (m in fc){
  print(m)
  curr = dplyr::filter(cov_wi_data, band_measure == m)
  if (pred == 'num'){
    fit = oneSamplePermutationTest(unlist(curr$type_diff_num))
  } else if (pred == 'bin') {
    fit = oneSamplePermutationTest(unlist(curr$type_diff_bin))
  } else {
    fit = oneSamplePermutationTest(unlist(curr$type_diff_spr))
  }
  
  print(summary(fit))
  cov_wi_ps = c(cov_wi_ps, fit$p.value)
  cov_wi_ts = c(cov_wi_ts, fit$statistic)
  cov_wi_df = c(cov_wi_df, fit$sample.size)
}
cov_wi_stats = data.frame(p = unlist(cov_wi_ps), f = unlist(cov_wi_ts), df = unlist(cov_wi_df), band_measure = fc, sigMC = p.adjust(cov_wi_ps, method = 'bonferroni') < 0.05, sig = cov_wi_ps < 0.05)
cov_wi_stats

```



## Which variables explain the most variance
# first show that none are significant
```{r}
pred = 'bin'
supp_flag = FALSE # are you using main measures, or supplemental measures


all_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/net_dem_data', detector, '.csv', sep=''))
all_data <- mutate(all_data, band_measure = tolower(paste(Frequency.Band, Measure, sep = '_')))
all_data[paste('str_beta_',pred,sep='')] = as.numeric(unlist(all_data[paste('str_beta_',pred,sep='')]))
if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    all_data = dplyr::filter(all_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    all_data = dplyr::filter(all_data, band_measure != m)
  }
}
fc = unique(all_data$band_measure)
for (m in fc){
  print(m)
  curr = dplyr::filter(all_data, band_measure == m)
  if (pred == 'num'){
    fit = aovp(data=curr, str_beta_num ~ locus + hem + race + gender + hand + age + Etiology + Lesional + SeizureAge + contacts + Institution)
  } else if (pred == 'bin') {
    fit = aovp(data=curr, str_beta_bin ~ locus + hand + race + gender + age + Etiology + Lesional + SeizureAge + contacts  + hem + Institution)
  } else {
    fit = aovp(data=curr, str_beta_spr ~ locus + hem + race + gender + hand + age + Etiology + Lesional + SeizureAge + contacts + Institution)
  }
  
  print(summary(fit))
}


```
# fit ridge regression
```{r}
pred = 'bin'
supp_flag = FALSE # are you using main measures, or supplemental measures
k=10

all_data = read.csv(paste('/Volumes/bassett-data/Jeni/RAM/group_analysis/win_', as.character(win), '/net_dem_data', detector, '.csv', sep=''))

# extra cleaning
all_data <- mutate(all_data, band_measure = tolower(paste(Frequency.Band, Measure, sep = '_')))
all_data[paste('str_beta_',pred,sep='')] = as.numeric(unlist(all_data[paste('str_beta_',pred,sep='')]))
all_data[c('age','Education','SeizureAge')] = as.numeric(unlist(all_data[c('age','Education','SeizureAge')]))
all_data$race = as.factor(all_data$race)
all_data[all_data$hem == '','hem'] = NaN
all_data[all_data$locus == '','locus'] = NaN

if (supp_flag){
  # loop through other measures and remove...probably a better way to do this
  for (m in keep_measures){
    all_data = dplyr::filter(all_data, band_measure != m)
  }
}else {
  for (m in supp_measures){
    all_data = dplyr::filter(all_data, band_measure != m)
  }
}

lambdas = list()
fc = unique(all_data$band_measure)
for (m in fc){
  print(m)
  curr = dplyr::filter(all_data, band_measure == m)
  curr = curr[!is.na(curr[,paste('str_beta_',pred,sep='')]),]
  curr = curr[,c('locus', 'hem', 'race', 'gender', 'age', 'Etiology', 'Lesional','SeizureAge',
                'contacts','Institution', 'hand','avg',paste('str_beta_',pred,sep=''))]
  curr = na.omit(curr)
  x = model.matrix(~locus + hem + race + gender + age + Etiology + Lesional + SeizureAge + contacts + Institution + hand + avg, curr)[, -1]
  groups = c(rep(1,each=7),rep(2,each=2),rep(3,each=3),rep(4,each=1),5,rep(6,each=10),rep(7,each=2),8,rep(9,each=2),rep(10,each=8),rep(11,each=3), 12)
  if (pred == 'num'){
    y = unlist(curr$str_beta_num)
  } else if (pred == 'bin') {
    y = unlist(curr$str_beta_bin)
  } else {
    y = unlist(curr$str_beta_spr)
  }
  fit_cv = cv.gglasso(x=x,y=y,group=groups,nfolds = k)
  fit = gglasso(x=x,y=y,group=groups,lambda=fit_cv$lambda.min)
  coeffs = coef(fit, s=fit$lambda.min)
  names = attr(coeffs,'dimnames')[[1]]
  coeffs = coeffs[coeffs>0]
  print(names[order(-abs(coeffs))])
  
}


```

Test normality
```{r fig.height=10, fig.width=10}

pred = 'spr'# bin or num or spr
aec_flag = 'aec$' # which aec do you want to EXCLUDE, orth or regular. The carrot mean "starts with", $                      means 'ends with'
coh_flag = '^coh' # 
plv_flag = '^plv$'

curr_measures = net_data[!grepl(aec_flag, net_data$Measure) & !grepl(coh_flag, net_data$Measure) & !grepl(plv_flag, net_data$Measure), 'band_measure']
bfc = unique(curr_measures)

par(mfrow=c(4,4))
for (m in bfc){
  curr <- filter(net_data, band_measure == m)
  qqPlot(unlist(curr[paste('str_beta_',pred,sep='')]),ylab=m)
}


```

Skew normality
```{r fig.height=10, fig.width=10}

pred = 'spr'# bin or num or spr
aec_flag = 'aec$' # which aec do you want to EXCLUDE, orth or regular. The carrot mean "starts with", $                      means 'ends with'
coh_flag = '^coh' # 
plv_flag = '^plv$'

curr_measures = net_data[!grepl(aec_flag, net_data$Measure) & !grepl(coh_flag, net_data$Measure) & !grepl(plv_flag, net_data$Measure), 'band_measure']
bfc = unique(curr_measures)

par(mfrow=c(4,4))
for (m in bfc){
  curr <- filter(net_data, band_measure == m)
  qqPlot(unlist(curr[paste('ti_beta_',pred,sep='')]),ylab=m)
}


```



SOZ normality
```{r fig.height=10, fig.width=10}

pred = 'spr'# bin or num or spr
aec_flag = 'aec$' # which aec do you want to EXCLUDE, orth or regular. The carrot mean "starts with", $                      means 'ends with'
coh_flag = '^coh' # 
plv_flag = '^plv$'

curr_measures = soz_data[!grepl(aec_flag, soz_data$Measure) & !grepl(coh_flag, soz_data$Measure) & !grepl(plv_flag, soz_data$Measure), 'band_measure']
bfc = unique(curr_measures)

par(mfrow=c(4,4))
for (m in bfc){
  curr <- filter(soz_data, band_measure == m)
  qqPlot(unlist(curr[paste('soz_diff_',pred,sep='')]),ylab=m)
}


```


